### 2014-02-28 paper/formal.tex
formal done; releasing lock

Consider the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
TSNI.
%
\Red{HERE}

\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

\begin{theorem}[Sequential specification language is TINI]
For any target language |targetLang nop|, |specLang seqf (targetLang
nop)| satisfies TINI.
\end{theorem}

>>>>

Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLang ML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|, we can write the
following program in the specification language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(when false diverge)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(when true diverge)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, however |ic1| will reduce (in two
steps) to |ic1 = iS ; fullconf 2 pub tS1 (IT diverge)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{}.
} then the |sec| thread's decision to diverge or not is directly leaked to a
public entitiy.

In certain cases, however, a TSNI-safe concurrent scheduling policy such as
|roundrobinf| cannot be considered without imposig a non-trivial burden on the
concrete implementation.
%
(Section~\ref{ref:real} describes a particular embedding with JavsScript as the
target language.)
%
Hence, we consider an alternative NI property---called termination insensitive
non-interference---that can also be upheld by sequential languages at the cost
of leaking one bit through (non)-termination.
%
\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language |(C, V, .->, erasef l)| is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2 member C| and |c1', c2' member V| if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |c1'|$, and
   $|c2| |.->|^* |c2'|$, then
   $|c1'| \approx_{|l|} |c2'|$.
\end{definition}

TSNI states that if we take two |l|-equivalent configurations, and both
configurations reduce to terminal configuration states (for which there are no
possible further transitions), then the end configurations are also
|l|-equivalent.
%
We highlight that this statement is much weaker than TSNI: it only states that
terminating programs do not leak sensitive data.

Nevertheless, we believe TINI to be a useful for many scenariors and thus we
show that our IFC language with the sequential scheduling policy |seqf|
satisfies TINI.
%
\begin{theorem}[Sequential specification language is TINI]
For any target language |targetLang nop|, |specLang seqf (targetLang
nop)| satisfies TINI.
\end{theorem}
